\begin{abstract}
\iffalse  
  Abstract here \ldots Remember to talk about the area, problem,
  solution, methodology, results, and take-away. In general, an abstract
  should only be one paragraph and on the order of 200 words.
\fi

Hadoop is a widely used computing framework and Docker is a popular container technology that emerged last year and then quickly adopted by a lot of commercial companies. This paper examines the combination of Hadoop with Docker container, explores how Docker container works in Hadoop, and analyzes the security issues solved by adopting the Docker container and those issues that are not solved or introduced by the Docker container.

Our analysis shows that the YARN NodeManager executes Docker commands to launch multiple Docker containers in order to perform Hadoop MapReduce jobs. This method provides isolated MapReduce Job runtime environments and thus protects the secrecy and integrity of the executed programs to a large extent. One reason is that the containers limit the damages caused by arbitrary code execution during MapReduce job execution time and prevent attackers on the compromised node from adding errors into job computations. Another reason is that the launched containers will be killed after it finishes the assigned tasks. However, the Docker container could not protect data integrity and secrecy of HDFS. This is because the Docker container requires Hadoop to run in the non-secure mode, disabling user authorization and credentials. The Docker container also introduces other security risks, for example, the problem of setuid, while the permission of Docker has to be changed to enable launching the Docker containers.

\end{abstract}
